---
title: "Week 2 Assignment"  
author: "Ahmed M. Kamel"  
output: html_document
---

These are the answers for the assignment needed to complete week 2.

###loading and processing data 

**Steps include**:  
1- *Setting working directory*  
2- *Converting dates using `as.Date()`*

```{r, echo=TRUE}
setwd("c:/users/ahmed/desktop")
df<- read.csv("activity.csv", na.strings="NA", header = T)
df$date<- as.Date(df$date, format = "%Y-%m-%d")
```

###What is mean total number of steps taken per day?
1- **calculate the total number of steps taken per day**

```{r}
dailydata<- tapply(df$steps, df$date, sum)
print(dailydata)

```

2- **Make a histogram of the total number of steps taken each day**

For this purpose, we need to calculate the total number of steps per day.  
A new variable called `dailydata` was computed for that purpose.
```{r Histogram, fig.height=4, fig.width=5}
hist(dailydata, 10, xlab="total number of steps per day", main = "Histogram")
```


3- **Mean and median steps per day**
```{r, echo=TRUE}
mean(dailydata, na.rm=T)
median(dailydata, na.rm=T)
```

###What is the average daily activity pattern? 
1-**Time series plot.**  

*I'll be using ggplot2 to construct this time series plot.  
*I'll calculate mean steps across intervals averaged across all days using `tapply()` after converting interval to a factor using `as.factor()`.
```{r, fig.width=5, fig.height=4}
library(ggplot2)
aggdf<- aggregate(df, list(as.factor(df$interval)), mean, na.rm=TRUE)
ggplot(aes(interval, steps), data= aggdf)+geom_line()+theme_bw()+
        labs(title="Line plot",subtitle="Interval (secs) vs. Steps")+xlab("Interval(secs)")+ylab("Steps")
```  

2-**5-mins interval with max. steps.**  
```{r}
x= aggdf$interval[which.max(aggdf$steps)]
```

The interval with max. number of steps is **`r x`**  

###Imputing missing values